---
title: "MachineLearningProject"
author: "Jun Yue"
date: "2022/2/23"
output: html_document
---
# **Synopsis**
Using data from accelerometers on the belt,forearm, arm, and dumbell of 6 perticipants who were asked to perform barbell lifts correctly and incorrectly in 5 different ways, we will predict the manner in which they did the exercise.
# **Getting data & Cleaning data**
## Load library
```{r}
library(caret);library(rpart);library(rpart.plot)
library(rattle);library(randomForest)
```
## Getting data
```{r}
train_data <- read.csv("./data/pml-training.csv")
test_data <- read.csv("./data/pml-testing.csv")
NAdata <- sapply(train_data,function(x)mean(is.na(x)))>.95
train_data <- train_data[,NAdata==F]
train_data <- train_data[,-c(1:7)]
train_nvz <- nearZeroVar(train_data)
train_data <- train_data[,-train_nvz]
train_data$classe <- as.factor(train_data$classe)
inTrain <- createDataPartition(y=train_data$classe,p=0.7,list = F)
training <- train_data[inTrain,];testing <- train_data[-inTrain,]

```
# **Predict Data by various models**
## Random forest
```{r}
modFit_RF <- randomForest(classe~.,data = training)
modFit_RF
predict_RF <- predict(modFit_RF,testing,type="class")
confusionMatrix(predict_RF,testing$classe)$overall
accuracy_RF <- round(confusionMatrix(predict_RF,testing$classe)$overall[[1]],3)
accuracy_RF
```    
## Generalized Boosted Model(gbm)
```{r}
control <- trainControl(method = "cv",number = 3,verboseIter = F)
modFit_GBM <- train(classe~.,data = training,method="gbm",trControl=control,verbose=F)
predict_GBM <- predict(modFit_GBM,testing)
confusionMatrix(predict_GBM,testing$classe)$overall
accuracy_GBM <- round(confusionMatrix(predict_GBM,testing$classe)$overall[[1]],3)
accuracy_GBM

```
## Decision Tree
```{r}
modFit_DT <- train(classe~.,data = training,method="rpart")
fancyRpartPlot(modFit_DT$finalModel)
```
```{r}
predict_DT <- predict(modFit_DT,testing)
confusionMatrix(predict_DT,testing$classe)$overall
accuracy_DT <- round(confusionMatrix(predict_DT,testing$classe)$overall[[1]],3)
accuracy_DT
```
## Results(Accuracy and Out of Sample Error)
```{r}
accuracy <- c(accuracy_RF,accuracy_GBM,accuracy_DT)
results <- data.frame(Model=c("RandomForest","GradientBoosted","DecisionTree"),Accuracy=accuracy,Oos_error=1-accuracy)
print(results)
```
###**The best model is the Random forest model,almost 100% accuracy.Let's use it to our test sets.**
## Predictions on Test set
```{r}
predict_test <- predict(modFit_RF,test_data)
predict_test
```












